---
title: 计算统计第一次课后作业
author: JunTao Sun
date: '2022-10-16'
slug: []
categories:
  - 计算统计
tags:
  - 作业
  - R
description: ~
featured_image: ~
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 4.1

## (a)

As the random variable X has pmd:$$p_1=\frac{1}{3},p_2=\frac{2}{3}$$

This can be accomplished by generating a random number U, and then setting

$$X=\begin{cases}1, if \; U < \frac{1}{3} \\ 2, if \; \frac{1}{3} \le U < 1 \end{cases}$$
We use R programming language for simulation.

```{r}
n=100
U=runif(n)
X=rep(0,n)
X[U<1/3]=1
X[U>1/3]=2
value<-sum(X==1)/n
```

According to the program, the proportion of values that are equal to 1 is `r round(value,2)`

## (b)

When n=1000,we can repeat the program:
```{r}
n=1000
U=runif(n)
X=rep(0,n)
X[U<1/3]=1
X[U>1/3]=2
value<-sum(X==1)/n
```

According to the program, the proportion of values that are equal to 1 is `r round(value,2)`

## (c)

When n=10000,we can repeat the program:
```{r}
n=10000
U=runif(n)
X=rep(0,n)
X[U<1/3]=1
X[U>1/3]=2
value<-sum(X==1)/n
```

According to the program, the proportion of values that are equal to 1 is `r round(value,2)`

# 4.3

As the random variable X has pmd:$$p\{X=1\}=0.3,p\{X=2\}=0.2,p\{X=3\}=0.15,p\{X=4\}=0.35$$

This can be accomplished by generating a random number U, and then setting

$$X=\begin{cases}1, if \; U < 0.3 \\ 2, if \; 0.3 \le U < 0.5 \\3, if \; 0.5 \le U < 0.65 \\4, if \; 0.65 \; \le U < 1 \end{cases}$$

```{r}
U=runif(1)
if (U<0.3) {
  X=1
}else if(U >= 0.3 & U <0.5) {
  X=2
}else if(U >= 0.5 & U <0.65) {
  X=3
}else if(U >= 0.65 & U <1) {
  X=4
}
```
According to the code, the value of that random variable X is:`r X`

# 5.3

As $F(x)=\frac{x^2+x}{2}, 0 \le x \le 1$,

Letting u = F(x) = \frac{x^2+x}{2}, we can get $x^2+x-2u=0$.

Solve for x as $x=\frac{-1+\sqrt{1+8u}}{2}$

Thus, we can generate random variables using the transformation $X=\frac{-1+\sqrt{1+8u}}{2}$, U is generated as a uniformly distributed over the interval (0,1)